RNA-seq from 4 cell populations

### 2020-08-21 deconvolution/fans4/molec_profiling.Rmd
Initial commit

geneCounts = df_featureCounts_gene[,7:ncol(df_featureCounts_gene)]
geneCounts = as.data.frame(geneCounts)
rownames(geneCounts) = geneInfo$Geneid

@@

```{r preprocess}
isexpr = rowSums(cpm(geneCounts)>1) >= 0.1*ncol(geneCounts)
table(isexpr)

@@

geneExpr = cpm(dge, log=TRUE)

@@

  isexpr = rowSums(cpm(geneCounts[,idx])>1) >= 0.3*ncol(geneCounts[,idx])
  table(isexpr)
  infoSub = droplevels(info[idx,])

@@

system("ml python; synapse add --parentid syn22243354 Roussos_MSSM_MolProf_FANS_4_diffExpression.RDS")
```

@@

file_SampleAttributesDS = "/sc/arion/projects/CommonMind/data/resources/GTEx/GTEx_Analysis_v8_Annotations_SampleAttributesDS.txt"
file_SubjectPhenotypesDS= "/sc/arion/projects/CommonMind/data/resources/GTEx/GTEx_Analysis_v8_Annotations_SubjectPhenotypesDS.txt"
file_counts = "/sc/arion/projects/CommonMind/data/resources/GTEx/GTEx_Analysis_2017-06-05_v8_RNASeQCv1.1.9_gene_reads.gct.gz"

@@

gtexColors = read.csv('/sc/arion/projects/CommonMind/data/resources/GTEx/GTEx_Tissue_colors.csv', header=TRUE)
```

@@

# full counts
file = '/hpc/users/hoffmg01/work/cmc_analysis/src/Roussos_MSSM_MolProf_FANS_4_geneCounts.csv.gz'
gz1 <- gzfile(file, "w")
write.table(data.table(EnsID = rownames(geneCounts), geneCounts), gz1, quote=FALSE, sep=",", row.names=FALSE)
close(gz1)

@@

# full counts
file = '/hpc/users/hoffmg01/work/cmc_analysis/src/Roussos_MSSM_MolProf_FANS_4_info.csv.gz'
gz1 <- gzfile(file, "w")
write.table(info, gz1, quote=FALSE, sep=",", row.names=FALSE)
close(gz1)

@@

>>>>

geneCounts = df_featureCounts_gene[,7:ncol(df_featureCounts_gene)]
geneCounts = as.matrix(geneCounts)
rownames(geneCounts) = geneInfo$Geneid

@@

```{r preprocess}
isexpr = rowSums(edgeR::cpm(geneCounts)>1) >= 0.1*ncol(geneCounts)
table(isexpr)

@@

geneExpr = edgeR::cpm(dge, log=TRUE)

@@

  isexpr = rowSums(edgeR::cpm(geneCounts[,idx])>1) >= 0.3*ncol(geneCounts[,idx])
  table(isexpr)
  infoSub = droplevels(info[idx,])

@@

# system("ml python; synapse add --parentid syn22243354 Roussos_MSSM_MolProf_FANS_4_diffExpression.RDS")
```

@@

# file_SampleAttributesDS = "/sc/arion/projects/CommonMind/data/resources/GTEx/GTEx_Analysis_v8_Annotations_SampleAttributesDS.txt"
file_SampleAttributesDS = synGet('syn22321103')$path

# file_SubjectPhenotypesDS= "/sc/arion/projects/CommonMind/data/resources/GTEx/GTEx_Analysis_v8_Annotations_SubjectPhenotypesDS.txt"
file_SubjectPhenotypesDS = synGet('syn22321104')$path

# file_counts = "/sc/arion/projects/CommonMind/data/resources/GTEx/GTEx_Analysis_2017-06-05_v8_RNASeQCv1.1.9_gene_reads.gct.gz"
file_counts = synGet('syn22321107')$path

@@

# file= '/sc/arion/projects/CommonMind/data/resources/GTEx/GTEx_Tissue_colors.csv'
file = synGet('syn22321106')$path
gtexColors = read.csv( file, header=TRUE)
```

@@

# full counts
file = 'Roussos_MSSM_MolProf_FANS_4_geneCounts.csv.gz'
gz1 <- gzfile(file, "w")
write.table(data.table(EnsID = rownames(geneCounts), geneCounts), gz1, quote=FALSE, sep=",", row.names=FALSE)
close(gz1)

@@

# full counts
file = 'Roussos_MSSM_MolProf_FANS_4_info.csv.gz'
gz1 <- gzfile(file, "w")
write.table(info, gz1, quote=FALSE, sep=",", row.names=FALSE)
close(gz1)

@@

# Differential expression
file = Roussos_MSSM_MolProf_FANS_4_diffExpression.RDS

nEXP_OBJ = File(file, 
                name = 'FANS4 Differential Expression results', 
                parentId = CODE$properties$id)
nEXP_OBJ = synStore(nEXP_OBJ, used = Ids, 
                    executed = thisFile)
